---
title: "MPG Difference by Auto/Manual"
author: "Junyoung Kim"
date: "Septermber 3, 2018"
output: 
    ioslides_presentation:
    widescreen: true
    smaller: true
    transition: faster
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly); library(ggplot2); library(gridExtra); library(kableExtra)
```

## Brief Summary {.smaller}
- Question: How do transmission types affect on fuel efficiency?
- Data: 1974 Motor Trend Car Road Tests
- Model: <b> ln(MPG) = β0 + β1 Transmission + β2 ln(Horsepower) + ε </b>
<center>
```{r}
head(mtcars, 10)
```
</center>

## Distribution {.smaller}
- Distribution of mpg(Miles per Gallon) is right-skewed.
- Taking log reshapes distribution more normal-like,
- And it reduces effects of possible outliers. 
```{r, echo=FALSE, fig.align="center" ,message=FALSE}
h <- ggplot(mtcars, aes(x=log(mpg))) + geom_histogram(bins=12, color="grey", fill="grey20")
h1 <- ggplotly(h, autosize = F, width = 500, height = 350) 
h1
```

## Linear Fit of Log-Log Model {.smaller}
- Taking logs on both sides of model linearizes the plot. 
- And it makes interpreting coefficients easier(percent by percent changes).
```{r}
# process
p <- plot_ly(data = mtcars, x = ~log(hp), y = ~log(mpg), color = I("black")) %>%
    add_markers(y = ~log(mpg), text = "log(mpg)", showlegend = FALSE) %>%
    add_lines(y = ~fitted(lm(log(mpg)~log(hp))), line = list(color = '#07A4B5'), name = "Linear") %>%
    add_lines(y = ~fitted(loess(log(mpg)~log(hp))), line = list(color = 'grey', dash = 'dash', shape = 'spline'), name = "Loess Smoother")
p
```


## Regression Results {.smaller}
```{r}
m1 <- lm(log(mpg)~as.factor(am)+log(hp), data=mtcars)
t1 <- as.table(round(summary(m1)$coef, 3))
dimnames(t1) <- list(c("Intercept", "Auto/Manual: 1", "log(Horsepower)"),
                     c("Coefficient", "Standard Error", "t-value", "p-value"))
knitr::kable(t1, caption = "Regression Results on log(MPG)") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```
<br> </br>

- Log(horsepower) shows a strong negative relation with log(mpg)(-0.459). 

- Auto/Manual holds a modreate positive coefficient(0.195). 

- Low p-values of both regressors(0.001, 0.000). 

- Log transform: The meaning of coefficient should be interpreted as changes in percent values: **for 1 percent increase of horsepower, mpg decreases approximately by 0.459 percent on average**.

## MPG Difference by Auto/Manual {.smaller}
- The transmission type(0 or 1) is not log-transformed.
- Manual transmissions(value = 1) have approximately 19.5%($100 * \beta_1$%) better fuel efficiency on average than automatic transmissions. 
```{r}
#---
mt <- mtcars
mt$tr <- as.factor(mtcars$am)
levels(mt$tr) <- c("Auto", "Manual")
#--- auto
hp.new <- min(mtcars$hp):max(mtcars$hp) # step1: new x values
am0 <- rep(0, length(hp.new)) # step2: new x2 values
data0 <- data.frame(hp.new, am0) # step3: combine x, x2
colnames(data0) <- c("hp", "am") # step4: make names the same as the model
y0 <- predict(m1, newdata=data0) # step5: predict y values = model outputs
#--- manual
data1 <- data.frame("hp"=hp.new, "am"=rep(1, length(hp.new))) # step2~4 at once
y1 <- predict(m1, newdata=data1) # step5: predict y values = model outputs

#---
p <- plot_ly(data =mt, x = ~log(hp), y = ~log(mpg), color = ~tr, colors = c("#56B1F7", "#132B43")) %>%
    add_markers(y = ~log(mpg), text = "log(mpg)", marker = list(size=10)) %>%
    add_lines(x = ~log(hp.new), y = ~y0, color = I("gray60"), name = "Auto Fit") %>%
    add_lines(x = ~log(hp.new), y = ~y1, color = I("black"), name = "Manual Fit")
p    
```

